{\LARGE Basis Choice for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-08 Paper/main.tex
Auto stash before merge of "main" and "origin/main"

	Then, the operator $K$ has orthonormal basis functions $\nu^{m} \in \mathbb{L}^{2}[0,1]$ each corresponding to an eigenvalue $\lambda^{m}$ since it is a positive compact self-adjoint operator (cf. \cite{alexanderian_KLexpansion_2015}).
	Theoretical considerations lead to the result that $X$ can be represented in the following form, called its Karhunen-Lo\'{e}ve expansion.\footnote{Proofs for these theorems are provided in Appendix \ref{Proof1} and \ref{Proof2}.} 
	\begin{equation}\label{KarhunenLoeve}
		X(\omega)(t) = \mu(t) + \sum_{m = 1}^{\infty} \xi^m(\omega) \nu^m(t), \quad \xi^m(\omega) =  \int_{0}^{1} \left(X(\omega)(s) - \mu(s)\right) \nu^m(s) \mathrm{d}s
	\end{equation}

@@

	As in the well known setting of principal component analysis, the eigenvalues correspond to the variance in the random function that is explained by the corresponding eigenfunction. 
	Therefore, ordering the the eigenfunctions according to their their corresponding eigenvalues $\lambda^{1} \geq \lambda^{2} \geq \dots \geq 0$ is useful for approximation purposes. Due to this property a functional observation can often be approximated well by using a limited number of the eigenfunctions of its generating random process.\\

@@

	In the following, we will call the $\hat{\nu}^m(s)$ functional principal components to distinguish the sample analogs from the theoretical eigenfunctions $\nu^m(s)$. As in the case of ordinary principal components, the number of functional principal components corresponding to non-zero eigenvalues is limited (cf. chapter 8.2.3 \cite{ramsay_functional_2005}). As each curve is infinite dimensional, there is no upper limit to this number due to the dimensionality. However, the number of curves still imposes an upper limit of $N-1$ non-zero eigenvalues, where $N$ is the number of curves in the data set.
	These sample analogs naturally lead to the following representation of each sample curve $x_i(t)$.
	\begin{equation}
		x_i(t) = \hat{\mu}(t) + \sum_{j = 1}^{N-1} \hat{\xi}_{i}^{m} \hat{\nu}^{m}(t)
	\end{equation}

@@

	In reality, these calculations are often done using basis representations of both the functional principal components $\hat{\nu}^m$ and the observations $x_i(t)$ leading to the following representation. For the sake of clarity, the following equation assumes that the bases used for the expansion of both the observations and the coefficient function are true bases of $\mathbb{L}^2[0,1]$ and can therefore be used to express the corresponding objects exactly.
	\begin{equation}\label{FPCA_basis_expansion}
		\begin{split}
			\hat{\xi}_{i}^m & = \int_{0}^{1} {\color{red}\left( x_i(s) - \hat{\mu}(s)\right)} {\color{blue}\hat{\nu}^m(s)} \mathrm{d}s
			= \int_{0}^{1} {\color{red}\left(\sum_{j \in \mathcal{I}} a_{i,j} \phi_j(s)\right)} {\color{blue}\left(\sum_{k \in \mathcal{L}} b_{k}^m \psi_{k}(s)\right)} \mathrm{d}s \\
			& = \int_{0}^{1} {\color{red}\left(\sum_{j = 1}^{J} a_{i,j} \phi_j(s) + \delta_i^J(s)\right)} {\color{blue}\left(\sum_{k = 1}^{K} b_{k}^m \psi_{k}(s) + \delta_{\beta}^K(s)\right)} \mathrm{d}s \\
			& = \sum_{j = 1}^{J} \left[a_{i,j}\sum_{k = 1}^{K} b_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s \right] +  \sum_{k = 1}^{K} b_{k}^m \int_{0}^{1} \delta_i^J(s) \psi_{k}(s) \mathrm{d}s + \sum_{j = 1}^{J} a_{i,j} \int_{0}^{1}\phi_j(s) \delta_{\beta}^K(s) \mathrm{d}s
		\end{split}
	\end{equation}

	In practice, a typical choice is to use the same basis $\left(\phi_j(t)\right)_{j \in \mathcal{I}}$ and the same truncation parameter $L$ for the basis expansion of the curves for both the demeaned observations $\left(x_i(t) - \hat{\mu}(t)\right)$ and the functional principal components $\hat{\nu}^m$. This leads to the following simplification of Equation \ref{FPCA_basis_expansion}.
	\begin{equation}\label{score_approx}
			\hat{\xi}_{i}^m = \sum_{j = 1}^{L} \left[a_{i,j}\sum_{k = 1}^{L} b_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s \right] +  \sum_{k = 1}^{L} b_{k}^m \int_{0}^{1} \delta_i^L(s) \psi_{k}(s) \mathrm{d}s + \sum_{j = 1}^{L} a_{i,j} \int_{0}^{1}\phi_j(s) \delta_{\beta}^L(s) \mathrm{d}s
	\end{equation}

@@

	This method of deriving or approximating the eigenfunctions and scores from a data set is introduced in \cite{ramsay_functional_2005} (chapter 8.4.2) and implemented in the R-package fda. The following considerations and results of the simulation study might therefore serve as information about the performance of this method in a scenario where a limited number of basis functions is provided to the method.

	\subsection{Scalar-on-Function Regression}
	In the simple scalar setting, one of the most important tools in econometrics is linear regression. Its goal is twofold: to gain information about the dependency between variables, but also to allow for prediction. To motivate the jump from multivariate regression to scalar-on-function regression, assume first a data generating process as follows.
	\begin{equation}
		Y = X\beta + \epsilon
	\end{equation}

@@

	The concept of linear regression can be extended to a setting of functional data, where a scalar response variable is assumed to be dependent of a functional regressor. 
	Even though integrating over the product of an observation with the coefficient function is not the only functional that can be used to create a data generating process involving functional observations, it is the most typical as it naturally extends the intuition from multiple linear regression to the realm of infinite-dimensional objects. Therefore, we will always assume a data generating process as follows in this paper.
	\begin{equation}\label{DGP}
		Y(\omega) = \alpha + \int_{0}^{1} \beta(s)X(\omega)(s) \mathrm{d}s + \epsilon(\omega)
	\end{equation}

	Here, $\beta(t)$ is an unknown coefficient function. Similar to the finite-dimensional setting, an interesting question is how to estimate $\beta(t)$ given a data set containing realizations of a random function and associated scalar response variables. However, a simple extension of the OLS estimator to allow for infinite-dimensional objects is not possible. Therefore, other options have to be considered.

	\subsubsection{Estimation using Basis-Representation}\label{basis_exp_transf}
	The most common way to make this problem tractable is via a basis representation of $\beta(t)$. Therefore, let $\{b_i(t) \: \vert \: i \in \mathcal{I}\}$ be a basis of $\mathbb{L}^2[0,1]$ and represent $\beta(t)$ in terms of this basis.
	\begin{equation}
		\beta(t) = \sum_{j \in \mathcal{I}} b_j \phi_j(t)
	\end{equation}

	This enables us to write equation \ref{DGP} with $\beta(t)$ represented in this way to obtain a formulation as a sum of scalar random variables $Z_j(\omega)$.
	\begin{equation}
		\begin{split}
			Y(\omega) & = \alpha + \int_{0}^{1} {\color{blue}\beta(s)} X(\omega)(s)\mathrm{d}s + \epsilon(\omega)
			= \alpha + \int_{0}^{1}\left[{\color{blue}\left(\sum_{j \in \mathcal{I}} b_j \phi_j(s)\right)} X(\omega)(s) \right]\mathrm{d}s + \epsilon(\omega) \\
			& = \alpha + \sum_{j \in \mathcal{I}} \left[b_j \textcolor{red}{\int_{0}^{1} X(\omega)(s) \phi_j(s)\mathrm{d}s}\right] + \epsilon(\omega)
		      = \alpha + \sum_{j \in \mathcal{I}} b_j \textcolor{red}{Z_j(\omega)} + \epsilon(\omega)
		\end{split}
	\end{equation}

@@

	A typical choice in this scenario is to use the same functional basis $\left(\phi_j(t)\right)_{j \in \mathcal{I}}$ and the same truncation parameter $L$ for both the coefficient function and the approximation of the observations. Defining the following notation 
	\begin{equation}
			\tilde{Z}_j(\omega) = \sum_{k = 1}^{L} \left[a_k(\omega) \int_{0}^{1} \phi_j(s) \phi_k(s) \mathrm{d}s \right] \quad j = 1, \dots, L
	\end{equation}

	This leads to a considerable simplification of Equation \ref{basis_exp_transf}.
	\begin{equation}\label{simplified_model_basis_equation}
		\begin{split}
			Y(\omega) &= \alpha + \sum_{j = 1}^{J} b_j \tilde{Z}_j(\omega) + \sum_{j = 1}^{J} b_j  \int_{0}^{1} \phi_j(s) \delta_{X}^{K}(\omega)(s) \mathrm{d}s + \sum_{k = 1}^{K} a_k  \int_{0}^{1} \delta_{\beta}^{J}(s)\phi_j(s) \mathrm{d}s + \epsilon(\omega) \\
			& \approx \alpha + \sum_{j = 1}^{J} b_j \tilde{Z}_j(\omega) + \epsilon(\omega)
		\end{split}
	\end{equation}

@@

	Using the Karhunen-Lo\'{e}ve Expansion to represent $X(\omega)$, it is also possible to express the data generating process in a slightly different way.
	\begin{equation}
		\begin{split}
			Y(\omega) &= \alpha + \int_{0}^{1} {\color{red}X(\omega)(s)} \beta(s) \mathrm{d}s + \epsilon(\omega)
			= \alpha + \int_{0}^{1} {\color{red}\left(\mu(s) + \sum_{m = 1}^{\infty} \xi^m(\omega) \nu^m(s)\right)} \beta(s) \mathrm{d}s + \epsilon(\omega)\\
			&= {\color{teal}\alpha + \int_{0}^{1} \mu(s) \beta(s) \mathrm{d}s} + \sum_{m = 1}^{\infty} \xi^m(\omega) {\color{violet}\int_{0}^{1} \nu^m(s) \beta(s) \mathrm{d}s} + \epsilon(\omega)
			= {\color{teal}\bar{\alpha}} + \sum_{m = 1}^{\infty} \xi^m(\omega) {\color{violet}\beta^m} + \epsilon(\omega)
		\end{split}
	\end{equation}

@@

	If we additionally derive and approximate the principal components and corresponding scores using a truncated basis representation as in Equation \ref{score_approx} we obtain the following. To not complicate things more than necessary, the following equation assumes that the same basis $\left(\phi_j(t)\right)_{j \in \mathcal{I}}$ was used in the derivation of the principal components and the expansion of the coefficient function. Additionally, the following approximation also truncates the basis for the expansion of the coefficient function at the same parameter $L$ that was used for the approximation of the principal components and scores.

@@

	The parameter $M \in \{1, \dots, N-1\}$ corresponds to the chosen number of principal components and therefore constitutes another choice in the approximation. Using only $M$ functional principal components therefore leads to the following approximation.
	\begin{equation}
		y_i \approx \tilde{\alpha}^L
		+ \sum_{m = 1}^{M} \left[ \tilde{\xi}^{m,L}_{i} {\color{red}\sum_{j = 1}^{L} b_j \int_{0}^{1} \tilde{\nu}^{m,L}(s) \phi_j(s) \mathrm{d}s} \right] + \epsilon_i 
		= \tilde{\alpha}^L
		+ \sum_{m = 1}^{M} \tilde{\xi}^{m,L}_{i} {\color{red}\bar{b}^{m,L}} + \epsilon_i
	\end{equation}

@@

	To exploit the regularity of the curves of the spectra, we introduced different basis functions in {\color{green} Link} and demonstrated the importance of the truncation parameter $K$ for the estimation in {\color{green} Link}. For the simulation study, we rely on the introduced estimation strategies with the introduced basis functions and focus on selecting the truncation parameter $K$ as well as the number of FPC, which is as well affected by $K$, by ten-fold cross-validation using the prediction mean-squared error. While cross-validation is common for selecting $K$, the number of FPC in practice is often truncated after a specified amount of explained variability \cite{kokoszka_introduction_2017}, which might not be optimal since FPC with smaller eigenvalues may have greater influence on the prediction (c.f \cite{Jolliffe_1982}). This might apply to this simulation too since certain eigenfunctions could correspond to certain chemical combinations and overtones in the absorption bands of the spectrum that could have high predictive power, but explain only little variability {\color{green} Link to NIR}.

@@

		where $Z \sim \mathcal{N}(0,1)$. In total, we created four combinations for the simulations, using the two true coefficient functions and the two sets of responses. These four combinations are then used with a different number of monomial basis functions $ \in \{1,2, \dots, 6\}$, cubic B-spline basis-function $\{5,6,...,18\}$ and Fourier functions $\{1,3,...,25\}$ to predict the generated responses using the basis expansion approach and the FPCR approach. For the evaluation, we used the prediction MSE calculated by 10 fold cross-validation.
		To obtain valid out of sample properties for the FPCR, within each of the ten ten-fold cross-validation splits, we first calculate the first $nharm$ FPC's for $nharm \in \{2,3,4\}$ of the training set $\mathcal{T}$ for each curve $i \in \{1,2, \dots, 200\}$, which was smoothed with the respective basis function specification. The obtained eigenfunctions $\nu^{m,\mathcal{T}}$ are then used to estimate the scores of the holdout set $\mathcal{H}$, $\hat{\xi}_{i}^{m, \mathcal{H}}$  by the equation
		\begin{equation}
			\begin{split}
				\hat{\xi}_{i}^{m, \mathcal{H},L} &\approx  \int_{0}^{1} {\color{red} \left(X_{i}^{\mathcal{H}}(s) - \hat{\mu}^{\mathcal{T}}(s)\right)} {\color{blue}\hat{\nu}^{m, \mathcal{T}} }\mathrm{d}s) 
			    = \int_{0}^{1} {\color{red}\left(\sum_{j = 1}^{L} a_{i,j}^{\mathcal{H}} \phi_j(s)\right)} {\color{blue}\left(\sum_{k = 1}^{L} b_{k}^{m, \mathcal{T}} \phi_{k}(s)\right)} \mathrm{d}s \\
				 &\approx \sum_{j = 1}^{L} \left[ a_{i,j}^{\mathcal{H}}\sum_{k = 1}^{L}  b_{k}^{m, \mathcal{T}} \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s\right]
			\end{split}
		\end{equation}

@@

	\subsubsection{Functional Principal Component Regression}
		The model which is used for the FPCR is described in \hyperref[fpc_exp_transf]{Estimation using Functional Principal Components}. Additionally to the selection of the truncation parameter $L$, the choice of the number of FPC's adds to the complexity of the model since the approximated eigenvalues and -functions from the decomposition are influenced by the choice of $L$ that was used to expand the function. But since the FPCR is ultimately estimated with a linear model with the FPC's as regressors, the relevant degrees of freedom in the estimation of the ultimate model are not affected by $K$, but only by the number of FPC's $n_{FPC} \in \{2, 3, 4 \}$. As will be described, it seems that neither a convex behavior of the MSPE, nor any clear relationship can be observed between the number of basis function and the number of FPC's. This might be because the dependency (FPCA is performed on the smoothed curves) is to complex to draw conclusions from this simulation study, therefore we will limit ourself to a brief description. In this simulation, the cross-validated choice of basis functions indicates that the FPCR might not take the differing signal-to-noise ratios of the responses into account since the FPC's, which affect the relevant degrees of freedom, are calculated solely from the smoothed curves, not considering the noise in the responses at all.

@@

	\subsection{Lemma} \label{Proof1}
	The curves $X(t) \in \mathbb{L}^2[0,1]$ is expanded by the eigenfunctions $\{\nu^m\}$ as Equation \ref{KarhunenLoeve}. The coefficients $\xi^{m}$ corresponding to eigenfunctions $\nu^m$ satisfy the following properties:

@@

		where $\delta^{m,n} = 1$ if $m = n$, otherwise 0. The result is produced from orthonormality of the eigenfunctions.

@@

		Let $K$ be a Hilbert-Schmidt operator as in Equation \ref{HSKernal}.We know that $K$ has a complete set of eigenfunctions ${\nu^m}$ in $\mathbb{L}^{2}[0,1]$  and non-negative eigenvalues $\lambda^m$ since $K$ is a positive compact self-adjoint operator. With the reminder that $\xi^m$ satisfy the three conclusions by Lemma \ref{Proof1}, we prove this expansion by considering

@@

		where the covariance function $c(t,s)$ has the Hilbert-Schmidt operator as in Equation \ref{HSKernal}. It turns out the product of the eigenfunction and the corresponding eigenvalue. For the last term, we derive from Equation \ref{Lemma2} that

>>>>

	Then, the operator $K$ has orthonormal basis functions $\nu^{m} \in \mathbb{L}^{2}[0,1]$ each corresponding to an Eigenvalue $\lambda^{m}$ since it is a positive compact self-adjoint operator (cf. \cite{alexanderian_KLexpansion_2015}).
	Theoretical considerations lead to the result that $X$ can be represented in the following form, called its Karhunen-Lo\'{e}ve expansion.\footnote{Proofs for these theorems are provided in Appendix \ref{Proof1} and \ref{Proof2}.} 
	\begin{equation}\label{KarhunenLoeve}
		X(\omega)(t) = \mu(t) + \sum_{m = 1}^{\infty} \xi^m(\omega) \nu^m(t), \quad \xi^m(\omega) =  \int_{0}^{1} \left(X(\omega)(s) - \mu(s)\right) \nu^m(s) \mathrm{d}s
	\end{equation}

@@

	As in the well known setting of principal component analysis, the Eigenvalues correspond to the variance in the random function that is explained by the corresponding Eigenfunction. 
	Therefore, ordering the the Eigenfunctions according to their their corresponding Eigenvalues $\lambda^{1} \geq \lambda^{2} \geq \dots \geq 0$ is useful for approximation purposes. Due to this property a functional observation can often be approximated well by using a limited number of the Eigenfunctions of its generating random process.\\

@@

	In the following, we will call the $\hat{\nu}^m(s)$ functional principal components to distinguish the sample analogs from the theoretical Eigenfunctions $\nu^m(s)$. As in the case of ordinary principal components, the number of functional principal components corresponding to non-zero Eigenvalues is limited (cf. chapter 8.2.3 \cite{ramsay_functional_2005}). As each curve is infinite dimensional, there is no upper limit to this number due to the dimensionality. However, the number of curves still imposes an upper limit of $N-1$ non-zero Eigenvalues, where $N$ is the number of curves in the data set.
	These sample analogs naturally lead to the following representation of each sample curve $x_i(t)$.
	\begin{equation}
		x_i(t) = \hat{\mu}(t) + \sum_{j = 1}^{N-1} \hat{\xi}_{i}^{m} \hat{\nu}^{m}(t)
	\end{equation}

@@

	In reality, these calculations are often implemented using basis representations of both the functional principal components $\hat{\nu}^m$ and the observations $x_i(t)$ leading to the following representation. For the sake of clarity, the following equation assumes that the bases used for the expansion of both the observations and the coefficient function are true bases of $\mathbb{L}^2[0,1]$ and can therefore be used to express the corresponding objects exactly.
	\begin{equation}\label{FPCA_basis_expansion}
		\begin{split}
			\hat{\xi}_{i}^m & = \int_{0}^{1} {\color{red}\left( x_i(s) - \hat{\mu}(s)\right)} {\color{blue}\hat{\nu}^m(s)} \mathrm{d}s
			= \int_{0}^{1} {\color{red}\left(\sum_{j \in \mathcal{I}} a_{i,j} \phi_j(s)\right)} {\color{blue}\left(\sum_{k \in \mathcal{L}} b_{k}^m \psi_{k}(s)\right)} \mathrm{d}s \\
			& = \int_{0}^{1} {\color{red}\left(\sum_{j = 1}^{J} a_{i,j} \phi_j(s) + \delta_i^J(s)\right)} {\color{blue}\left(\sum_{k = 1}^{K} b_{k}^m \psi_{k}(s) + \delta_{\beta}^K(s)\right)} \mathrm{d}s \\
			& = \sum_{j = 1}^{J} \left[a_{i,j}\sum_{k = 1}^{K} b_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s \right] +  \sum_{k = 1}^{K} b_{k}^m \int_{0}^{1} \delta_i^J(s) \psi_{k}(s) \mathrm{d}s + \sum_{j = 1}^{J} a_{i,j} \int_{0}^{1}\phi_j(s) \delta_{\beta}^K(s) \mathrm{d}s
		\end{split}
	\end{equation}

	In practice, a typical choice is to use the same basis $\left(\phi_j(t)\right)_{j \in \mathcal{I}}$ and the same truncation parameter $L$ for the basis expansion of the demeaned observations $\left(x_i(t) - \hat{\mu}(t)\right)$ and the functional principal components $\hat{\nu}^m$. This leads to the following simplification of Equation \ref{FPCA_basis_expansion}.
	\begin{equation}\label{score_approx}
			\hat{\xi}_{i}^m = \sum_{j = 1}^{L} \left[a_{i,j}\sum_{k = 1}^{L} b_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s \right] +  \sum_{k = 1}^{L} b_{k}^m \int_{0}^{1} \delta_i^L(s) \psi_{k}(s) \mathrm{d}s + \sum_{j = 1}^{L} a_{i,j} \int_{0}^{1}\phi_j(s) \delta_{\beta}^L(s) \mathrm{d}s
	\end{equation}

@@

	This method of deriving or approximating the Eigenfunctions and scores from a data set is introduced in \cite{ramsay_functional_2005} (chapter 8.4.2) and implemented in the R-package fda. The following considerations and results of the simulation study might therefore serve as information about the performance of this method in a scenario where a limited number of basis functions is provided to the method.

	\subsection{Scalar-on-Function Regression}
	In the simple scalar setting, one of the most important tools in econometrics is linear regression. Its goal is twofold: to gain information about the dependency between variables, but also to allow for prediction. To motivate the jump from multivariate regression to scalar-on-function regression, assume a data generating process as follows.
	\begin{equation}
		Y = X\beta + \epsilon
	\end{equation}

@@

	The concept of linear regression can be extended to a setting of functional data, where a scalar response variable is assumed to be dependent on a functional regressor. 
	Even though integrating over the product of an observation with the coefficient function is not the only functional that can be used to create a data generating process involving functional observations, it is the most typical as it naturally extends the intuition from multiple linear regression to the realm of infinite-dimensional objects. Therefore, we will always assume a data generating process as follows in this paper.
	\begin{equation}\label{DGP}
		Y(\omega) = \alpha + \int_{0}^{1} \beta(s)X(\omega)(s) \mathrm{d}s + \epsilon(\omega)
	\end{equation}

	Similar to the finite-dimensional setting, an interesting question is how to estimate the unknown coefficient function $\beta(t)$ given a data set containing realizations of a random function and associated scalar response variables. However, a simple extension of the OLS estimator to allow for infinite-dimensional objects is not possible. Therefore, other options have to be considered, two of which will be explained in the following.

	\subsubsection{Estimation using Basis-Representation}\label{basis_exp_transf}
	The most common way to make this problem tractable is via a basis representation of $\beta(t)$. Therefore, let $\{\phi_i(t) \: \vert \: i \in \mathcal{I}\}$ be a basis of $\mathbb{L}^2[0,1]$ and represent $\beta(t)$ in terms of this basis.
	\begin{equation}
		\beta(t) = \sum_{j \in \mathcal{I}} b_j \phi_j(t)
	\end{equation}

	This enables us to write equation \ref{DGP} using this representation to obtain a formulation as a sum of scalar random variables $Z_j(\omega)$.
	\begin{equation}
		\begin{split}
			Y(\omega) & = \alpha + \int_{0}^{1} {\color{blue}\beta(s)} X(\omega)(s)\mathrm{d}s + \epsilon(\omega)
			= \alpha + \int_{0}^{1}\left[{\color{blue}\left(\sum_{j \in \mathcal{I}} b_j \phi_j(s)\right)} X(\omega)(s) \right]\mathrm{d}s + \epsilon(\omega) \\
			& = \alpha + \sum_{j \in \mathcal{I}} \left[b_j \textcolor{red}{\int_{0}^{1} X(\omega)(s) \phi_j(s)\mathrm{d}s}\right] + \epsilon(\omega)
		      = \alpha + \sum_{j \in \mathcal{I}} b_j \textcolor{red}{Z_j(\omega)} + \epsilon(\omega)
		\end{split}
	\end{equation}

@@

	A typical choice in this scenario is to use the same functional basis $\left(\phi_j(t)\right)_{j \in \mathcal{I}}$ and the same truncation parameter $L$ for both the coefficient function and the approximation of the observations. Using the following notation 
	\begin{equation}
			\tilde{Z}_j(\omega) = \sum_{k = 1}^{L} \left[a_k(\omega) \int_{0}^{1} \phi_j(s) \phi_k(s) \mathrm{d}s \right] \quad j = 1, \dots, L
	\end{equation}

	this leads to a considerable simplification of Equation \ref{basis_exp_transf}.
	\begin{equation}\label{simplified_model_basis_equation}
		\begin{split}
			Y(\omega) &= \alpha + \sum_{j = 1}^{J} b_j \tilde{Z}_j(\omega) + \sum_{j = 1}^{J} b_j  \int_{0}^{1} \phi_j(s) \delta_{X}^{K}(\omega)(s) \mathrm{d}s + \sum_{k = 1}^{K} a_k  \int_{0}^{1} \delta_{\beta}^{J}(s)\phi_j(s) \mathrm{d}s + \epsilon(\omega) \\
			& \approx \alpha + \sum_{j = 1}^{J} b_j \tilde{Z}_j(\omega) + \epsilon(\omega)
		\end{split}
	\end{equation}

@@

	Using the Karhunen-Lo\'{e}ve Expansion to represent $X(\omega)$, it is also possible to express the data generating process in terms of the Eigenfunctions of $X(\omega)(t)$.
	\begin{equation}
		\begin{split}
			Y(\omega) &= \alpha + \int_{0}^{1} {\color{red}X(\omega)(s)} \beta(s) \mathrm{d}s + \epsilon(\omega)
			= \alpha + \int_{0}^{1} {\color{red}\left(\mu(s) + \sum_{m = 1}^{\infty} \xi^m(\omega) \nu^m(s)\right)} \beta(s) \mathrm{d}s + \epsilon(\omega)\\
			&= {\color{teal}\alpha + \int_{0}^{1} \mu(s) \beta(s) \mathrm{d}s} + \sum_{m = 1}^{\infty} \xi^m(\omega) {\color{violet}\int_{0}^{1} \nu^m(s) \beta(s) \mathrm{d}s} + \epsilon(\omega)
			= {\color{teal}\bar{\alpha}} + \sum_{m = 1}^{\infty} \xi^m(\omega) {\color{violet}\beta^m} + \epsilon(\omega)
		\end{split}
	\end{equation}

@@

	If we additionally derive and approximate the principal components and corresponding scores using a truncated basis representation as in Equation \ref{score_approx} we obtain the following. To not complicate things more than necessary, the following equation assumes that the same basis $\left(\phi_j(t)\right)_{j \in \mathcal{I}}$ was used in the derivation of the principal components and the expansion of the coefficient function. Additionally, the following approximation truncates the basis for the expansion of the coefficient function at the same parameter $L$ that was used for the approximation of the principal components and scores.

@@

	The parameter $M \in \{1, \dots, N-1\}$ corresponds to the chosen number of principal components and therefore constitutes another choice in the approximation. Using only $M$ functional principal components leads to the following approximation.
	\begin{equation}
		y_i \approx \tilde{\alpha}^L
		+ \sum_{m = 1}^{M} \left[ \tilde{\xi}^{m,L}_{i} {\color{red}\sum_{j = 1}^{L} b_j \int_{0}^{1} \tilde{\nu}^{m,L}(s) \phi_j(s) \mathrm{d}s} \right] + \epsilon_i 
		= \tilde{\alpha}^L
		+ \sum_{m = 1}^{M} \tilde{\xi}^{m,L}_{i} {\color{red}\bar{b}^{m,L}} + \epsilon_i
	\end{equation}

@@

	To exploit the regularity of the curves of the spectra, we introduced different basis functions in {\color{green} Link} and demonstrated the importance of the truncation parameter $K$ for the estimation in {\color{green} Link}. For the simulation study, we rely on the introduced estimation strategies with the introduced basis functions and focus on selecting the truncation parameter $K$ as well as the number of FPC, which is as well affected by $K$, by ten-fold cross-validation using the prediction mean-squared error. While cross-validation is common for selecting $K$, the number of FPC in practice is often truncated after a specified amount of explained variability \cite{kokoszka_introduction_2017}, which might not be optimal since FPC with smaller Eigenvalues may have greater influence on the prediction (c.f \cite{Jolliffe_1982}). This might apply to this simulation too since certain Eigenfunctions could correspond to certain chemical combinations and overtones in the absorption bands of the spectrum that could have high predictive power, but explain only little variability {\color{green} Link to NIR}.

@@

		where $Z \sim \mathcal{N}(0,1)$. In total, we created four combinations for the simulations, using the two true coefficient functions and the two sets of responses. These four combinations are then used with a different number of monomial basis functions $ \in \{1,2, \dots, 6\}$, cubic B-spline basis-function $\{5,6,...,18\}$ and Fourier functions $\{1,3,...,25\}$ to predict the generated responses using the basis expansion approach and the FPCR approach. For the evaluation, we used the prediction MSE calculated by 10 fold cross-validation.
		To obtain valid out of sample properties for the FPCR, within each of the ten ten-fold cross-validation splits, we first calculate the first $nharm$ FPC's for $nharm \in \{2,3,4\}$ of the training set $\mathcal{T}$ for each curve $i \in \{1,2, \dots, 200\}$, which was smoothed with the respective basis function specification. The obtained Eigenfunctions $\nu^{m,\mathcal{T}}$ are then used to estimate the scores of the holdout set $\mathcal{H}$, $\hat{\xi}_{i}^{m, \mathcal{H}}$  by the equation
		\begin{equation}
			\begin{split}
				\hat{\xi}_{i}^{m, \mathcal{H},L} &\approx  \int_{0}^{1} {\color{red} \left(X_{i}^{\mathcal{H}}(s) - \hat{\mu}^{\mathcal{T}}(s)\right)} {\color{blue}\hat{\nu}^{m, \mathcal{T}} }\mathrm{d}s) 
			    = \int_{0}^{1} {\color{red}\left(\sum_{j = 1}^{L} a_{i,j}^{\mathcal{H}} \phi_j(s)\right)} {\color{blue}\left(\sum_{k = 1}^{L} b_{k}^{m, \mathcal{T}} \phi_{k}(s)\right)} \mathrm{d}s \\
				 &\approx \sum_{j = 1}^{L} \left[ a_{i,j}^{\mathcal{H}}\sum_{k = 1}^{L}  b_{k}^{m, \mathcal{T}} \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s\right]
			\end{split}
		\end{equation}

@@

	\subsubsection{Functional Principal Component Regression}
		The model which is used for the FPCR is described in \hyperref[fpc_exp_transf]{Estimation using Functional Principal Components}. Additionally to the selection of the truncation parameter $L$, the choice of the number of FPC's adds to the complexity of the model since the approximated Eigenvalues and -functions from the decomposition are influenced by the choice of $L$ that was used to expand the function. But since the FPCR is ultimately estimated with a linear model with the FPC's as regressors, the relevant degrees of freedom in the estimation of the ultimate model are not affected by $K$, but only by the number of FPC's $n_{FPC} \in \{2, 3, 4 \}$. As will be described, it seems that neither a convex behavior of the MSPE, nor any clear relationship can be observed between the number of basis function and the number of FPC's. This might be because the dependency (FPCA is performed on the smoothed curves) is to complex to draw conclusions from this simulation study, therefore we will limit ourself to a brief description. In this simulation, the cross-validated choice of basis functions indicates that the FPCR might not take the differing signal-to-noise ratios of the responses into account since the FPC's, which affect the relevant degrees of freedom, are calculated solely from the smoothed curves, not considering the noise in the responses at all.

@@

	\subsection{Lemma} \label{Proof1}
	The curves $X(t) \in \mathbb{L}^2[0,1]$ is expanded by the Eigenfunctions $\{\nu^m\}$ as Equation \ref{KarhunenLoeve}. The coefficients $\xi^{m}$ corresponding to Eigenfunctions $\nu^m$ satisfy the following properties:

@@

		where $\delta^{m,n} = 1$ if $m = n$, otherwise 0. The result is produced from orthonormality of the Eigenfunctions.

@@

		Let $K$ be a Hilbert-Schmidt operator as in Equation \ref{HSKernal}.We know that $K$ has a complete set of Eigenfunctions ${\nu^m}$ in $\mathbb{L}^{2}[0,1]$  and non-negative Eigenvalues $\lambda^m$ since $K$ is a positive compact self-adjoint operator. With the reminder that $\xi^m$ satisfy the three conclusions by Lemma \ref{Proof1}, we prove this expansion by considering

@@

		where the covariance function $c(t,s)$ has the Hilbert-Schmidt operator as in Equation \ref{HSKernal}. It turns out the product of the Eigenfunction and the corresponding Eigenvalue. For the last term, we derive from Equation \ref{Lemma2} that
